A Bioconductor workflow for processing and analysing spatial proteomics data

### 2018-04-16 bioc-workflow-annotated.tex

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\end{alltt}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: 'combine' is deprecated.\\\#\# Use 'gtable\_combine' instead.\\\#\# See help("{}Deprecated"{})}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in `[[<-.data.frame`(`*tmp*`, i, value = structure(list(t = numeric(0), : replacement has 0 rows, data has 10}}\begin{alltt}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
##   pubMedIds: 26754106 
## Annotation:  
## - - - Processing information - - -
## Combined [5489,10] and [6268,10] MSnSets Tue Apr 10 11:36:36 2018 
## Subset [6725,20][5032,20] Tue Apr 10 11:36:36 2018 
## Removed features with more than 0 NAs: Tue Apr 10 11:36:36 2018 
## Dropped featureData's levels Tue Apr 10 11:36:36 2018 
## Subset [5032,20][5032,20] Tue Apr 10 14:00:41 2018 
## Removed features with more than 0 NAs: Tue Apr 10 14:00:41 2018 
## Dropped featureData's levels Tue Apr 10 14:00:41 2018 
## Subset [5032,20][5032,20] Tue Apr 10 16:11:22 2018 
## Removed features with more than 0 NAs: Tue Apr 10 16:11:22 2018 
## Dropped featureData's levels Tue Apr 10 16:11:22 2018 
## Subset [5032,20][5032,20] Tue Apr 10 16:17:52 2018 
## Removed features with more than 0 NAs: Tue Apr 10 16:17:52 2018 
## Dropped featureData's levels Tue Apr 10 16:17:52 2018 
## Subset [5032,20][5032,20] Tue Apr 10 16:25:51 2018 
## Removed features with more than 0 NAs: Tue Apr 10 16:25:51 2018 
## Dropped featureData's levels Tue Apr 10 16:25:51 2018 
## Subset [5032,20][5032,20] Tue Apr 10 16:29:26 2018 
## Removed features with more than 0 NAs: Tue Apr 10 16:29:26 2018 
## Dropped featureData's levels Tue Apr 10 16:29:27 2018 
## Subset [5032,20][5032,20] Tue Apr 10 16:35:47 2018 
## Removed features with more than 0 NAs: Tue Apr 10 16:35:47 2018 
## Dropped featureData's levels Tue Apr 10 16:35:47 2018 
## Subset [5032,20][5032,20] Tue Apr 10 16:47:20 2018 
## Removed features with more than 0 NAs: Tue Apr 10 16:47:20 2018 
## Dropped featureData's levels Tue Apr 10 16:47:20 2018 
##  MSnbase version: 2.5.9
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
##   pubMedIds: 26754106 
## Annotation:  
## - - - Processing information - - -
## Combined [5489,10] and [6268,10] MSnSets Tue Apr 10 11:36:36 2018 
## Subset [6725,20][5032,20] Tue Apr 10 11:36:36 2018 
## Removed features with more than 0 NAs: Tue Apr 10 11:36:36 2018 
## Dropped featureData's levels Tue Apr 10 11:36:36 2018 
## Subset [5032,20][5032,20] Tue Apr 10 14:00:41 2018 
## Removed features with more than 0 NAs: Tue Apr 10 14:00:41 2018 
## Dropped featureData's levels Tue Apr 10 14:00:41 2018 
## Subset [5032,20][5032,20] Tue Apr 10 16:11:22 2018 
## Removed features with more than 0 NAs: Tue Apr 10 16:11:22 2018 
## Dropped featureData's levels Tue Apr 10 16:11:22 2018 
## Subset [5032,20][5032,20] Tue Apr 10 16:17:52 2018 
## Removed features with more than 0 NAs: Tue Apr 10 16:17:52 2018 
## Dropped featureData's levels Tue Apr 10 16:17:52 2018 
## Subset [5032,20][5032,20] Tue Apr 10 16:25:51 2018 
## Removed features with more than 0 NAs: Tue Apr 10 16:25:51 2018 
## Dropped featureData's levels Tue Apr 10 16:25:51 2018 
## Subset [5032,20][5032,20] Tue Apr 10 16:29:26 2018 
## Removed features with more than 0 NAs: Tue Apr 10 16:29:26 2018 
## Dropped featureData's levels Tue Apr 10 16:29:27 2018 
## Subset [5032,20][5032,20] Tue Apr 10 16:35:47 2018 
## Removed features with more than 0 NAs: Tue Apr 10 16:35:47 2018 
## Dropped featureData's levels Tue Apr 10 16:35:47 2018 
## Subset [5032,20][5032,20] Tue Apr 10 16:47:20 2018 
## Removed features with more than 0 NAs: Tue Apr 10 16:47:20 2018 
## Dropped featureData's levels Tue Apr 10 16:47:20 2018 
## Subset [5032,20][5032,20] Tue Apr 10 16:52:54 2018 
## Removed features with more than 0 NAs: Tue Apr 10 16:52:54 2018 
## Dropped featureData's levels Tue Apr 10 16:52:54 2018 
##  MSnbase version: 2.5.9
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\subsection*{Features of interest}
In addition to adding annotation using the \texttt{addMarkers}
function, one can store specific sets of proteins by using the
\textit{Features of interest} infrastructure from the
\Biocpkg{MSnbase} package. If users have specific subsets of proteins
they wish to highlight in their data (possibly across multiple
experiments) they would first create a \texttt{FeaturesOfInterest}
object \hl{and then use the \textit{highlightOnPlot} function to 
visualise these}. For example, if we wanted to highlight \st{a} 
proteins with the accession numbers Q8CG48, Q8CG47, Q8K2Z4, and Q8C156, 
which are some of the proteins known to form part of the 13S condensin complex, 
we \hl{would call the following code:}

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{prots} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Q8CG48"}\hlstd{,} \hlstr{"Q8CG47"}\hlstd{,} \hlstr{"Q8K2Z4"}\hlstd{,} \hlstr{"Q8C156"}\hlstd{)}
\hlstd{foi13s} \hlkwb{<-} \hlkwd{FeaturesOfInterest}\hlstd{(}\hlkwc{description} \hlstd{=} \hlstr{"13S consensin proteins"}\hlstd{,}
                             \hlkwc{fnames} \hlstd{= prots,}
                             \hlkwc{object} \hlstd{= hl)}
\hlstd{foi13s}
\end{alltt}
\begin{verbatim}
## Traceable object of class "FeaturesOfInterest"
##  Created on Tue Apr 10 16:52:56 2018 
##  Description:
##   13S consensin proteins
##  4 features of interest:
##    Q8CG48, Q8CG47, Q8K2Z4, Q8C156
\end{verbatim}
\begin{alltt}
\hlkwd{plot2D}\hlstd{(hl)}
\hlkwd{addLegend}\hlstd{(hl,} \hlkwc{cex} \hlstd{=} \hlnum{.6}\hlstd{)}
\hlkwd{highlightOnPlot}\hlstd{(hl, foi13s)}
\end{alltt}
\end{kframe}
\includegraphics[width=.8\textwidth]{figure/foi-1}

@@

Direct comparisons of individual channels in replicated experiments
do\st{es} not provide an adequate, goal-driven assessment of different
experiments. Indeed, due to the nature of the experiment and gradient
fraction collection, the quantitative channels do not correspond to
identical selected fractions along the gradient. For example, in the
table below (taken from \texttt{hl}'s \texttt{pData}) TMT channels
127C (among others) in both replicates originate from different sets
of gradient fractions (gradient fractions 7 - 9 and 8 - 9 for each
replicate, respectively). Different sets of gradient fractions are
often pooled to obtain enough material and optimise acurate
quantitation.

% latex table generated in R 3.5.0 by xtable 1.8-2 package
% Tue Apr 10 16:52:56 2018
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Tue Apr 10 16:52:55 2018 
## Added markers from  'pdres' marker vector. Tue Apr 10 16:52:56 2018 
##  MSnbase version: 2.5.10
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{svmf} \hlkwb{<-} \hlkwd{dir}\hlstd{(extdatadir,} \hlkwc{full.names} \hlstd{=} \hlnum{TRUE}\hlstd{,}
              \hlkwc{pattern} \hlstd{=} \hlstr{"bpw-svmopt.rds"}\hlstd{)}
\hlstd{params} \hlkwb{<-} \hlkwd{readRDS}\hlstd{(svmf)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{(ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{))}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4323379               0.3037630               0.3822328 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6930642               0.6014878               0.4426545 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4224179               0.5978957               0.9497788 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7950203               0.7117761               0.3147679 
##         Plasma membrane              Proteasome 
##               0.7042806               0.4150910
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4323379               0.3037630               0.3822328 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6930642               0.6014878               0.4426545 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4224179               0.5978957               0.9497788 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7950203               0.7117761               0.3147679 
##         Plasma membrane              Proteasome 
##               0.7042806               0.4150910
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      85                     170                      84 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     301                     478                      99 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      27                     123                     523 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     230                     341                      38 
##         Plasma membrane              Proteasome                 unknown 
##                     322                     154                    2057
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlstd{MSnbase}\hlopt{::}\hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
##   pubMedIds: 26754106 
## Annotation:  
## - - - Processing information - - -
## Combined [5489,10] and [6268,10] MSnSets Wed Apr 11 14:03:28 2018 
##  MSnbase version: 2.5.9
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
##   pubMedIds: 26754106 
## Annotation:  
## - - - Processing information - - -
## Combined [5489,10] and [6268,10] MSnSets Wed Apr 11 14:03:28 2018 
## Subset [6725,20][5032,20] Wed Apr 11 14:03:28 2018 
## Removed features with more than 0 NAs: Wed Apr 11 14:03:28 2018 
## Dropped featureData's levels Wed Apr 11 14:03:28 2018 
##  MSnbase version: 2.5.9
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\subsection*{Features of interest}
In addition to adding annotation using the \texttt{addMarkers}
function, one can store specific sets of proteins by using the
\textit{Features of interest} infrastructure from the
\Biocpkg{MSnbase} package. If users have specific subsets of proteins
they wish to highlight in their data (possibly across multiple
experiments) they would first create a \texttt{FeaturesOfInterest}
object \hl{and then use the \textit{highlightOnPlot} function to 
visualise these}. For example, if we wanted to highlight 
proteins with the accession numbers Q8CG48, Q8CG47, Q8K2Z4, and 
Q8C156, which are some of the proteins known to form part of the 
13S condensin complex, we \hl{would call the following code:}

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{prots} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Q8CG48"}\hlstd{,} \hlstr{"Q8CG47"}\hlstd{,} \hlstr{"Q8K2Z4"}\hlstd{,} \hlstr{"Q8C156"}\hlstd{)}
\hlstd{foi13s} \hlkwb{<-} \hlkwd{FeaturesOfInterest}\hlstd{(}\hlkwc{description} \hlstd{=} \hlstr{"13S consensin proteins"}\hlstd{,}
                             \hlkwc{fnames} \hlstd{= prots,}
                             \hlkwc{object} \hlstd{= hl)}
\hlstd{foi13s}
\end{alltt}
\begin{verbatim}
## Traceable object of class "FeaturesOfInterest"
##  Created on Wed Apr 11 14:03:30 2018 
##  Description:
##   13S consensin proteins
##  4 features of interest:
##    Q8CG48, Q8CG47, Q8K2Z4, Q8C156
\end{verbatim}
\begin{alltt}
\hlkwd{plot2D}\hlstd{(hl)}
\hlkwd{addLegend}\hlstd{(hl,} \hlkwc{cex} \hlstd{=} \hlnum{.6}\hlstd{)}
\hlkwd{highlightOnPlot}\hlstd{(hl, foi13s)}
\end{alltt}
\end{kframe}
\includegraphics[width=.8\textwidth]{figure/foi-1}

@@

Direct comparisons of individual channels in replicated experiments
do not provide an adequate, goal-driven assessment of different
experiments. Indeed, due to the nature of the experiment and gradient
fraction collection, the quantitative channels do not correspond to
identical selected fractions along the gradient. For example, in the
table below (taken from \texttt{hl}'s \texttt{pData}) TMT channels
127C (among others) in both replicates originate from different sets
of gradient fractions (gradient fractions 7 - 9 and 8 - 9 for each
replicate, respectively). Different sets of gradient fractions are
often pooled to obtain enough material and optimise acurate
quantitation.

% latex table generated in R 3.5.0 by xtable 1.8-2 package
% Wed Apr 11 14:03:30 2018
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Wed Apr 11 14:03:29 2018 
## Added markers from  'pdres' marker vector. Wed Apr 11 14:03:30 2018 
##  MSnbase version: 2.5.10
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

We can plot the results using the \texttt{plot2D} function (Figure
\ref{fig:plotPDres}).

@@

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{(ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{))}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4318484               0.3059444               0.3846145 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6952120               0.6096139               0.4308645 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4099447               0.5950343               0.9499410 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7954586               0.7096376               0.3119884 
##         Plasma membrane              Proteasome 
##               0.7244522               0.4199965
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4318484               0.3059444               0.3846145 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6952120               0.6096139               0.4308645 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4099447               0.5950343               0.9499410 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7954586               0.7096376               0.3119884 
##         Plasma membrane              Proteasome 
##               0.7244522               0.4199965
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      85                     173                      87 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     298                     472                     103 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      26                     124                     521 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     229                     346                      38 
##         Plasma membrane              Proteasome                 unknown 
##                     317                     155                    2058
\end{verbatim}
\end{kframe}
\end{knitrout}
